\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Stefano Quartuccio} \\[7.5pt]
\href{https://github.com/Lutifya}{\raisebox{-0.05\height}\faGithub\ Lutifya} \ $|$ \ 
\href{https://www.linkedin.com/in/stefanoquartuccio/}{\raisebox{-0.05\height}\faLinkedin\ stefanoquartuccio} \ $|$ \ 
\href{https://www.google.com/maps/place/Giussano,+Italy}{\raisebox{-0.05\height}\faGlobe \ Giussano, Italy} \ $|$ \ 
\href{mailto:stefano.quartuccio@outlook.com}{\raisebox{-0.05\height}\faEnvelope \ stefano.quartuccio@outlook.com} \ $|$ \ 
\href{tel:+393756046195}{\raisebox{-0.05\height}\faMobile \ +39\,375\,604\,6195} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Master's student in Data Science with a strong focus on Artificial Intelligence and Large Language Models. Currently completing a thesis on a RAG-based semantic search engine that includes fine-tuning a 20-billion-parameter language model. Passionate about building robust, efficient, and cutting-edge solutions that combine academic rigor with hands-on software engineering.

%Experience
\section{Work Experience}

\begin{joblong}{Software Engineer, Elibra srl.}{May 2022 -- present / Italy}
\item Backend development and maintenance within an Agile (Scrum) product team.
\item Daily use of Spring Boot, Maven, TDD, and systematic refactoring to ensure code quality and reliability.
\item Full SDLC ownership including Git-based workflows, algorithmic analysis, debugging, and deployment activities.
\item Managed infrastructure automation with Ansible playbooks and maintained reproducible scenario-based environments for development and testing.
\end{joblong}

\begin{jobshort}{Junior Web Developer, Rc-info srl.}{Apr 2021 -- Apr 2022 / Italy}
Supported company projects with full-stack web development, evolving features across client and server components.
\end{jobshort}

\begin{jobshort}{iOS/Android Junior Developer, PlayTime Mobile \textregistered srl.}{Feb 2020 -- Aug 2020 / Italy}
Collaborated on cross-platform mobile application development during internship.
\end{jobshort}

\begin{jobshort}{Junior Developer (Internship), Link-up srl.}{Dec 2018 -- Dec 2019 / Italy}
Supported software development activities while learning company IT processes.
\end{jobshort}
  
%Projects
\section{Projects}

\begin{itemize}[leftmargin=1.25em]
    \item \textbf{Master's Thesis -- Enhancing Legal Workflows: Design and Evaluation of a RAG-Based Semantic Search Engine}: Built an end-to-end legal RAG platform combining multilingual E5 embeddings, vector database retrieval, and a GPT-OSS 20B LLM fine-tuned with LoRA on synthetic, human-validated datasets; delivered higher accuracy than baseline systems and outlined safeguards for privacy-preserving deployments. %\href{https://github.com/Lutifya}{Highlights}
\end{itemize}

\begin{itemize}[leftmargin=1.25em]
    \item \href{https://huggingface.co/Lutifya/gpt-oss-20b-q5_0}{Fine-tuned GPT-OSS-20B (Q5	extunderscore0)}: Publicly released GGUF quantized on Q5\_0 enabling legal-domain inference on resource-constrained hardware.
\end{itemize}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}} 	
2022 -- Oct 2025 & Master's Degree in Data Science, \textbf{University of Milano-Bicocca} \\ 

2019 -- 2022 & Bachelor's Degree in Informatics, \textbf{University of Milano-Bicocca} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
% \section{Publications}
% \begin{refsection}[citations.bib]
% \nocite{*}
% \printbibliography[heading=none]
% \end{refsection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming Languages &  \normalsize{\textbf{Experienced:} Python, Java \quad \textbf{Familiar:} JavaScript, PHP, Bash, Scheme}\\
AI / ML Libraries  &  \normalsize{PyTorch, Scikit-learn, Pandas, NumPy, Hugging Face Transformers, LangChain}\\  
AI / ML Concepts & \normalsize{Natural Language Processing, Retrieval-Augmented Generation (RAG), LLM Fine-tuning, Vector Databases, Semantic Search}\\
Frameworks \& Tools & \normalsize{Spring Boot, Maven, Git, Docker, Agile (Scrum), Jira}\\
Languages & \normalsize{\textbf{Native:} Italian \quad \textbf{Fluent:} English}\\
\end{tabularx}

%----------------------------------------------------------------------------------------

\par\bigskip\hrule\bigskip

\begin{center}
    {\scriptsize I authorize the processing of my personal data pursuant to Article 13 of Legislative Decree 30 June 2006 n\textdegree{}196 -- ``Code regarding the protection of personal data'' and Article 13 of GDPR 679/16 -- ``European regulation on the protection of personal data''.}
\end{center}


\end{document}
